Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-01-31 2017-GECCO-Modeling-User-Interactions-in-IEC/sample-sigconf.tex
bib folder created

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings\footnote{This is an abstract footnote}. 
\end{abstract}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}

>>>>

\begin{abstract}
The necessary intervention of humans in interactive evolutionary
computational systems has inherent drawbacks arising from the very nature of 
the algorithms, namely, the human fatigue caused by the interaction, and
the boredom arising when users evaluate a large number of artifacts 
many of which are not interesting or are very similar to each other.
To tackle these issues, in this paper we
propose a human-centered framework to model 
the complex interactions on these system.
Three case studies are presented where the model is applied in the 
development of evolutionary interactive systems, with different techniques:
volunteer-collaborative, unplugged and sensor-based. 
Both conceptual and implementation details are provided where the   
technique is applied to measure and increase user engagement and participation.
Our experiments show that the model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc,../bib/biblio}
